---
title: "The Right to Vote - Introduction"
author: "Prof. Jonathan Cervas"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Franklin on Voting Rights

> Today a man owns a jackass worth fifty dollars and he is entitled to vote; but before the next election the jackass dies. The man in the meantime has become more experienced, his knowledge of the principles of government, and his acquaintance with mankind, are more extensive, and he is therefore better qualified to make a proper selection of rulers—but the jackass is dead and the man cannot vote.

> Now gentlemen, pray inform me, in whom is the right of suffrage? In the man or in the jackass?

Benjamin Franklin


## Moral Arc of History

```{r}
y <- seq(0.02,1,0.0235)
y <- y^2
years <- seq(1776, 2022, 6)
imaginary.data <- (y-min(y))/(max(y)-min(y))

plot(1, type = "n", xlab = "",
     ylab = "Suffrage (%)", xlim = c(1776, 2022), 
     ylim = c(0, 1), axes=F)
			axis(side=2, las=2, at=seq(0, 1, 0.25), labels=paste0(seq(0,100, 25), "%"))
			axis(side=1, las=2, at=seq(1776, 2022, 6), labels=seq(1776, 2022, 6), cex.axis=0.6)
			box(col="black")
			lines(years, imaginary.data)
```

## Punctuated Equilibrium?

```{r}
years <- seq(1776, 2022, 6)
imaginary.data <- c(rep(0.25, 24), rep(0.5,8), rep(1,10))

plot(1, type = "n", xlab = "",
     ylab = "Suffrage (%)", xlim = c(1776, 2022), 
     ylim = c(0, 1), axes=F)
			axis(side=2, las=2, at=seq(0, 1, 0.25), labels=paste0(seq(0,100, 25), "%"))
			axis(side=1, las=2, at=seq(1776, 2022, 6), labels=seq(1776, 2022, 6), cex.axis=0.6)
			box(col="black")
			lines(years, imaginary.data)
```

## Punctuated but with Gradual Periods

```{r}
years <- seq(1776, 2022, 6)
imaginary.data <- c(rep(0.25, 24), rep(0.5,8), seq(0.5,1,0.055))

plot(1, type = "n", xlab = "",
     ylab = "Suffrage (%)", xlim = c(1776, 2022), 
     ylim = c(0, 1), axes=F)
			axis(side=2, las=2, at=seq(0, 1, 0.25), labels=paste0(seq(0,100, 25), "%"))
			axis(side=1, las=2, at=seq(1776, 2022, 6), labels=seq(1776, 2022, 6), cex.axis=0.6)
			box(col="black")
			lines(years, imaginary.data)
```


```{r}

years <- seq(1790, 1850, 6)
pop <- c(4, 10, 20)

plot(1, type = "n", xlab = "",
     ylab = "U.S. Population", xlim = c(1790, 1850), 
     ylim = c(0, 25), axes=F)
			axis(side=2, las=2, at=seq(0, 25, 5), labels=paste0(seq(0, 25, 5), " Mil"))
			axis(side=1, las=1, at=years, labels=years, cex.axis=0.85)
			box(col="black")
			lines(c(1790,1820,1850), pop)
```

