---
title: "The Right to Vote?"
author: "Prof. Jonathan Cervas"
affiliation: Carnegie Mellon University
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  tufte::tufte_handout: default
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
bibliography: /Users/cervas/Downloads/library.bib
biblio-style: apsr
geometry: margin=1in
# fontfamily: libertine
fontsize: 11pt
# spacing: double

endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

The right to vote is sacred in the United States; or is it? As we will learn over the next several weeks, the voting public has expanded from a narrow set of individuals, to a larger share of residents. But, who is enfranchised has been contested throughout U.S. history, including in modern America.

## Question I

What do you imagine the _actual_ trajectory of voting rights to be?

```{r, fig-fullwidth, fig.width = 7, fig.height = 4.5, fig.fullwidth = TRUE, warning=FALSE, message=FALSE, cache=FALSE, out.width='100%'}
plot(1, type = "n", xlab = "",
     ylab = "Suffrage (%)", xlim = c(1776, 2022), 
     ylim = c(0, 1), axes=F)
      axis(side=2, las=2, at=seq(0, 1, 0.25), labels=paste0(seq(0,100, 25), "%"), cex.axis=1)
      axis(side=1, las=2, at=seq(1776, 2022, 6), labels=seq(1776, 2022, 6), cex.axis=0.8)
      box(col="black")
      abline(h=seq(0,1,0.25), lty=2, lwd = .5, col="gray40") 
```

## Question II (90 seconds)

In 2024, the U.S. will hold a presidential election. But not everyone *can* or *should* be allowed to participate. Make a list of **three** individuals, classes of people, or groups which should **not** be allowed to vote in Pennsylvania.

1) 

2) 

3)  

## Question III (90 seconds)

In 2024, the U.S. will hold a presidential election. But not everyone *can* or *should* be allowed to participate. Make a list of **three** individuals, classes of people, or groups which should **not** be allowed to vote in Pennsylvania. _Wait for instruction_.

1) 

2) 

3)  

## Discussion

How do your lists compare to those seated next to you? Compare your lists to 3-5 other students. 

Are there any individuals or groups that everyone has included on these lists? 

Do you have unique entries on your lists? Discuss with your group why you think there is some agreement and some that differ. 

For those where there is less agreement, contemplate why either they, or you, believe this group should not be given the right to vote in the presidential election.

Are there other context in which this list would change? Would the same exclusions apply for state-level elections, like for governor? How about local elections, such as school board?

## Directions

Open a blank text file. Type:

1) your name, 
2) today's date, 
3) "Voting Rights and Representation", and 
4) "Assignment 1" on four consecutive lines. 

In this document, either scan (ie., take a picture) of your worksheet and paste it into the document, or repeat your list from Question II in the document. 

Save the document, and by Friday at 11:59p upload it to Canvas. You can submit this in the assignment "In-class exercise - Assignment 1".
